Fixing Vulnerabilities Hinders Maintainability

### 2019-02-06 paper/ICPC19/icpc19.tex
review sec II

Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately. In the example (Listing~\ref{lst:vuln}), all functions receive as
input the SSL session, \texttt{s}. In the \texttt{dtls1\_reassemble\_fragment}
function the size of the fragment \texttt{msg\_hdr-$>$frag\_off+frag\_len} is
checked against the handshake message size \texttt{msg\_hdr->msg\_len} (line
$13$) and then against the maximum size allowed in a DTLS handshake message for
\texttt{s} (line $16$-$21$). However, it is not verified if \texttt{msg\_hdr->msg\_len}
is lower than the size allowed by DTLS. Thus, in line
$37$, when \texttt{msg\_len} is allocated to the fragment buffer, more memory
than the allowed might be allocated. According to the commit message, $10$
handshake messages are allowed per DTLS connection. Hence, a remote attacker
could leverage this issue to trigger memory allocations corresponding to large
length values and lead the system to memory exhaustion that could end in a DoS
attack. The code changes performed to fix the vulnerability were the following:

>>>>

Every SSL/TLS connection begins with a handshake which is responsible by the
negotiation between two parties. DTLS provides a mechanism for fragmenting a
handshake message over a number of packets, each of which can be transmitted
separately. In the example (Listing~\ref{lst:vuln}), all functions receive as
input the SSL session, \texttt{s}.\Luis{is the previous sentence relevant?.} In
the \texttt{dtls1\_reassemble\_fragment} function the size of the fragment
\texttt{msg\_hdr-$>$frag\_off+frag\_len} is checked against the handshake
message size \texttt{msg\_hdr->msg\_len} (line $13$) and then against the
maximum size allowed in a DTLS handshake message for \texttt{s} (line
$16$-$21$).\Luis{I'm not sure about my comment: I think it could be easier if
we explain the previous sentence in pure natural language. These kind of
statements \texttt{msg\_hdr-$>$frag\_off+frag\_len} are not easy to process in
this context.} However, it is not verified if \texttt{msg\_hdr->msg\_len} is
lower than the size allowed by DTLS\Luis{did not understand the problem of not
checking the minimum.}. Thus, in line $37$, when \texttt{msg\_len} is allocated
to the fragment buffer, more memory than the allowed might be allocated.
According to the commit message, $10$ handshake messages are allowed per DTLS
connection. Hence, a remote attacker could leverage this issue to trigger
memory allocations corresponding to large length values and lead the system to
memory exhaustion that could end in a DoS attack.\Luis{I'm not happy with this
paragraph. It's difficult to process and I dont think a reviewer will actually
spend a lot of energy to understand this. (Ignore this if you find it clear.)}
The code changes performed to fix the vulnerability were the following:
